\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{url}
\usepackage{hyperref}
\lstdefinestyle{mystyle}{
    basicstyle=\small\ttfamily,   
    breaklines=true,                          
    numbers=left,                    
}
\lstset{style=mystyle}
\author{Pascal Cotret, \href{mailto:pascal.cotret@gmail.com}{pascal.cotret@gmail.com}}
\title{ISBNtools for Mediawiki}    
\date{}
\begin{document}
\maketitle
\vspace{-.5cm}
\section*{Introduction}
This document is a tutorial to use a custom based on the wonderful \texttt{isbntools} package in order to import ISBN references in a Mediawiki-like syntax. Two short tutorials are given with related codes:
\begin{enumerate}
\item Importing a list of references from an input file.
\item Importing a single reference.
\end{enumerate}
\section{Prerequisites}
Tested on an Ubuntu machine. (yes, we know\ldots We're working on a Windows version !)
\begin{enumerate}
\item \texttt{sudo apt-get install python-pip}
\item \texttt{sudo pip install isbntools}
\end{enumerate}\newpage
\section{Tutorials}
\subsection{Importing from a list}
\subsubsection{Prerequisites}
\begin{itemize}
\item You have a Python script \texttt{listimport.py} (see code section below). 
\item You have a file \texttt{input.txt} with all your ISBNs (one per line). 
\end{itemize}
\subsubsection{Example}
\textbf{Input file (input.txt):}
\begin{lstlisting}
9780470474242
9780201440997
\end{lstlisting}

\noindent \textbf{Command (parameter after the Python script is books' owner):}
\begin{lstlisting}
python listimport.py pascal
\end{lstlisting}

\noindent \textbf{Output (mediawiki.txt):}
\begin{lstlisting}
| Cryptography Engineering: Design Principles And Practical Applications || Kohno, Tadayoshi || Wiley Pub., inc. || 2010 || [http://isbndb.com/search/all?query=9780470474242 9780470474242] || pascal
|-
| Computer Security: Art And Science || Bishop, Matt || Addison-Wesley || 2004 || [http://isbndb.com/search/all?query=9780201440997 9780201440997] || pascal
|-
\end{lstlisting}
\newpage
\subsection{Importing a single book}
\subsubsection{Prerequisites}
\begin{itemize}
\item You have a Python script \texttt{singleimport.py} (see code section below). 
\item You have an ISBN number to add (10 or 13 digits).
\end{itemize}
\subsubsection{Example}
\textbf{Command:}
\begin{lstlisting}
python simpleimport.py pascal 9780470474242 
\end{lstlisting}

\noindent \textbf{Parameters:}
\begin{enumerate}
\item Books' owner.
\item ISBN number.
\end{enumerate}   

\noindent \textbf{Output (mediawiki.txt):}
\begin{lstlisting}
| Cryptography Engineering: Design Principles And Practical Applications || Kohno, Tadayoshi || Wiley Pub., inc. || 2010 || [http://isbndb.com/search/all?query=9780470474242 9780470474242] || pascal
|-
\end{lstlisting}
\newpage
\section{Code}
\subsection{listimport.py}
\lstinputlisting{listimport.py}
\subsection{singleimport.py}
\lstinputlisting{singleimport.py}
\section{Sources}
\url{https://pypi.python.org/pypi/isbntools}\\
\url{https://www.mediawiki.org/wiki/MediaWiki/fr}
\end{document}